### 2019-02-21 paper_01_fluidfft/article.tex
Update template and python dependencies
sed 's/section\*/section/g' article.tex
Subsection -> paragraphbf sed -i 's/subsubsection/paragraphbf/g' */article.tex
Overview etc. as sections and sub+other divisions sed -i 's/section\{/subsection\{/g' */article.tex sed -i 's/subsection[{].[[:alnum:]]. /section\{/g' */article.tex
Include fluidfft paper and prettify

\documentclass{../jors}

\begin{document}

{\bf Software paper for submission to the Journal of Open Research Software} \\

To complete this template, please replace the blue text with your own. The
paper has three main sections: (1) Overview; (2) Availability; (3) Reuse
potential.

Please submit the completed paper to: editor.jors@ubiquitypress.com

\rule{\textwidth}{1pt}

\section*{(1) Overview}

\vspace{0.5cm}

\section*{Title}

% \textcolor{blue}{The title of the software paper should focus on the software,
% e.g. “Text mining software from the X project”. If the software is closely
% linked to a specific research paper, then “Software from Paper Title” is
% appropriate. The title should be factual, relating to the functionality of the
% software and the area it relates to rather than making claims about the
% software, e.g. “Easy-to-use”.}

FluidFFT: common API (C++ and Python) for Fast Fourier Transform HPC libraries

\section*{Paper Authors}

% \textcolor{blue}{1. Last name, first name; (Lead/corresponding author first) \\
% 2. Last name, first name; etc.}

1. MOHANAN Ashwin Vishnu$^a$\\
2. BONAMY Cyrille$^b$\\
3. AUGIER Pierre$^b$\\

\smallskip

$^a$ Linn\'e Flow Centre, Department of Mechanics, KTH, 10044 Stockholm, Sweden.
$^b$ Univ. Grenoble Alpes, CNRS, Grenoble INP\footnote{Institute of Engineering
Univ. Grenoble Alpes}, LEGI, 38000 Grenoble, France.\\

\section*{Paper Author Roles and Affiliations}
% \textcolor{blue}{1. First author role and affiliation \\
% 2. Second author role and affiliation etc.}

1. Ph.D. student, Linn\'e Flow Centre, KTH Royal Institute of Technology,
Sweden; \\
2. Research Engineer, LEGI, Universit\'e Grenoble Alpes, CNRS, France; \\
3. Researcher, LEGI, Universit\'e Grenoble Alpes, CNRS, France

\section*{Abstract}

@@

The Python package \fluidpack{fft} provides a common Python API for performing
Fast Fourier Transforms (FFT) in sequential, in parallel and on GPU with different
FFT libraries (FFTW, P3DFFT, PFFT, cuFFT). \fluidpack{fft} is a comprehensive FFT
framework which allows Python users to easily and efficiently perform FFT and the
associated tasks, such as as computing linear operators and energy spectra.
%
We describe the architecture of the package composed of C++ and Cython FFT
classes, Python ``operator'' classes and Pythran functions.
%
The package supplies utilities to easily test itself and benchmark the different
FFT solutions for a particular case and on a particular machine.
%
We present a performance scaling analysis on three different computing clusters
and a microbenchmark showing that \fluidpack{fft} is an interesting solution to
write efficient Python applications using FFT.

\section*{Keywords}

% \textcolor{blue}{keyword 1; keyword 2; etc. \\
% Keywords should make it easy to identify who and what the software will be
% useful for.}

Free and open-source library; Python; Fast Fourier Transform; Distributed; MPI;
GPU; High performance computing%

\section*{Introduction}

@@

\section*{Implementation and architecture}

@@

\subsection*{C++ API}

@@

\subsection*{Python API} Similar to other packages in the FluidDyn project,
\fluidpack{fft} also uses an object-oriented approach, providing FFT classes.
%
This is in contrast with the approach adopted by \pack{numpy.fft} and \pack{%
scipy.fftpack} which provides functions instead, with which the user has to
figure out the procedure to design the input values and to use the return
values, from the documentation.
%
In \fluidpack{fft}, the Python API wraps all the functionalities of its C++
counterpart and offers a richer experience through an accompanying
operator class.

@@

\subsection*{Code organization}
\begin{figure}[htp]
  \centering
  \includegraphics[width=0.96\linewidth]{Pyfig/fig_build_use}
  \caption{Flowchart illustrating how the C++ and Python API are built and used
  for one particular class, viz. \codeinline{FFT2DMPIWithFFTWMPI2D}. The dotted
  arrows in C++ part stand for include statements, demonstrating the class
  hierarchy and in the Python part indicate how different codes are imported. On
  the bottom, a smaller flowchart demonstrates how to use the API by writing user
  code.  }\label{fig:build_use}
\end{figure}

@@

\subsection*{Performance}

\subsubsection*{Scalability tests using \codeinline{fluidfft-bench}}

@@

\subsubsection*{Microbenchmark of critical ``operator'' functions}

@@

\section*{Quality control}

@@

\section*{(2) Availability}
\vspace{0.5cm}
\section*{Operating system}

@@

\section*{Programming language}

@@

\section*{Dependencies}

% \textcolor{blue}{E.g. libraries, frameworks, incl. minimum version
% compatibility.}
C++ API:
\begin{itemize}
  \item{\bf Optional:} \pack{OpenMPI} or equivalent, \libpack{FFTW},
    \libpack{P3DFFT}, \libpack{PFFT} and \libpack{cuFFT} libraries.
\end{itemize}

@@

\section*{List of contributors}

@@

\section*{Software location:}

% {\bf Archive} \textcolor{blue}{(e.g. institutional repository, general
% repository) (required – please see instructions on journal website for
% depositing archive copy of software in a suitable repository)}

@@

\section*{Language}

@@

\section*{(3) Reuse potential}

@@

\section*{Acknowledgements}

@@

\section*{Funding statement}

@@

\section*{Competing interests}

@@

% \section*{References}

@@

\bibliographystyle{../agsm}
\bibliography{../bib}

\rule{\textwidth}{1pt}

{\bf Copyright Notice} \\
Authors who publish with this journal agree to the following terms: \\

>>>>

% \documentclass{../jors}

% {\bf Software paper for submission to the Journal of Open Research Software} \\
%
% To complete this template, please replace the blue text with your own. The
% paper has three main sections: (1) Overview; (2) Availability; (3) Reuse
% potential.
%
% Please submit the completed paper to: editor.jors@ubiquitypress.com
%
% \rule{\textwidth}{1pt}
%
\section{Overview}
%
% \vspace{0.5cm}
%
% \subsection{Title}
%
% % \textcolor{blue}{The title of the software paper should focus on the software,
% % e.g. “Text mining software from the X project”. If the software is closely
% % linked to a specific research paper, then “Software from Paper Title” is
% % appropriate. The title should be factual, relating to the functionality of the
% % software and the area it relates to rather than making claims about the
% % software, e.g. “Easy-to-use”.}
%
% FluidFFT: common API (C++ and Python) for Fast Fourier Transform HPC libraries
%
% \subsection{Paper Authors}
%
% % \textcolor{blue}{1. Last name, first name; (Lead/corresponding author first) \\
% % 2. Last name, first name; etc.}
%
% 1. MOHANAN Ashwin Vishnu$^a$\\
% 2. BONAMY Cyrille$^b$\\
% 3. AUGIER Pierre$^b$\\
%
% \smallskip
%
% $^a$ Linn\'e Flow Centre, Department of Mechanics, KTH, 10044 Stockholm, Sweden.
% $^b$ Univ. Grenoble Alpes, CNRS, Grenoble INP\footnote{Institute of Engineering
% Univ. Grenoble Alpes}, LEGI, 38000 Grenoble, France.\\
%
% \subsection{Paper Author Roles and Affiliations}
% % \textcolor{blue}{1. First author role and affiliation \\
% % 2. Second author role and affiliation etc.}
%
% 1. Ph.D. student, Linn\'e Flow Centre, KTH Royal Institute of Technology,
% Sweden; \\
% 2. Research Engineer, LEGI, Universit\'e Grenoble Alpes, CNRS, France; \\
% 3. Researcher, LEGI, Universit\'e Grenoble Alpes, CNRS, France

% \subsection{Abstract}

@@

% The Python package \fluidpack{fft} provides a common Python API for performing
% Fast Fourier Transforms (FFT) in sequential, in parallel and on GPU with different
% FFT libraries (FFTW, P3DFFT, PFFT, cuFFT). \fluidpack{fft} is a comprehensive FFT
% framework which allows Python users to easily and efficiently perform FFT and the
% associated tasks, such as as computing linear operators and energy spectra.
% %
% We describe the architecture of the package composed of C++ and Cython FFT
% classes, Python ``operator'' classes and Pythran functions.
% %
% The package supplies utilities to easily test itself and benchmark the different
% FFT solutions for a particular case and on a particular machine.
% %
% We present a performance scaling analysis on three different computing clusters
% and a microbenchmark showing that \fluidpack{fft} is an interesting solution to
% write efficient Python applications using FFT.
%
% \subsection{Keywords}
%
% % \textcolor{blue}{keyword 1; keyword 2; etc. \\
% % Keywords should make it easy to identify who and what the software will be
% % useful for.}
%
% Free and open-source library; Python; Fast Fourier Transform; Distributed; MPI;
% GPU; High performance computing%
%
\subsection{Introduction}

@@

\subsection{Implementation and architecture}

@@

\subsubsection{C++ API}

@@

\subsubsection{Python API} Similar to other packages in the FluidDyn project,
\fluidpack{fft} also uses an object-oriented approach, providing FFT classes.
%
This is in contrast with the approach adopted by \pack{numpy.fft} and \pack{%
scipy.fftpack} which provides functions instead, with which the user has to
figure out the procedure to design the input values and to use the return
values, from the documentation.
%
In \fluidpack{fft}, the Python API wraps all the functionalities of its C++
counterpart and offers a richer experience through an accompanying
operator class.

@@

\subsubsection{Code organization}
\begin{figure}[htp]
  \centering
  \includegraphics[width=0.96\linewidth]{Pyfig/fig_build_use}
  \caption{Flowchart illustrating how the C++ and Python API are built and used
  for one particular class, viz. \codeinline{FFT2DMPIWithFFTWMPI2D}. The dotted
  arrows in C++ part stand for include statements, demonstrating the class
  hierarchy and in the Python part indicate how different codes are imported. On
  the bottom, a smaller flowchart demonstrates how to use the API by writing user
  code.  }\label{fig:build_use}
\end{figure}

@@

\subsubsection{Performance}

\paragraphbf{Scalability tests using \codeinline{fluidfft-bench}}

@@

\paragraphbf{Microbenchmark of critical ``operator'' functions}

@@

\subsection{Quality control}

@@

\section{Availability}
\vspace{0.5cm}
\subsection{Operating system}

@@

\subsection{Programming language}

@@

\subsection{Dependencies}

% \textcolor{blue}{E.g. libraries, frameworks, incl. minimum version
% compatibility.}
\paragraph{C++ API:}
\begin{itemize}
  \item{\bf Optional:} \pack{OpenMPI} or equivalent, \libpack{FFTW},
    \libpack{P3DFFT}, \libpack{PFFT} and \libpack{cuFFT} libraries.
\end{itemize}

@@

\subsection{List of contributors}

@@

\subsection{Software location}

\paragraph{\bf Archive}
% {\bf Archive} \textcolor{blue}{(e.g. institutional repository, general
% repository) (required – please see instructions on journal website for
% depositing archive copy of software in a suitable repository)}

@@

\subsection{Language}

@@

\section{Reuse potential}

@@

\subsection*{Acknowledgements}

@@

\subsection*{Funding statement}

@@

\subsection*{Competing interests}

@@

% \subsection{References}

@@

% \rule{\textwidth}{1pt}
\vspace{10pt}
\hrule
\vspace{10pt}

\paragraphbf{Copyright Notice}

Authors who publish with this journal agree to the following terms:
